---
output: github_document
editor_options: 
  chunk_output_type: console
---

# Load up the required libraries

```{r}
library(lakemorpho)
library(raster)
library(sp)
library(rgdal)
library(gdalUtils)
library(rgeos)
```

# Read in vector files  

```{r}
tst_1lakes <- readOGR("example_data", "tst_1lakes")
```

# Read in DEM

The ESRI raster needs to be converted to something the Raster package can handle.
Here I am using `gdalUtilities::gdal_translate` to convert to a tif

```{r}
gdal_translate("example_data/tst_dem3k/", "example_data/tst_dem3k.tif")
tst_dem <- raster("example_data/tst_dem3k.tif")
```

# Crop DEM to extent of lake buffer
This step isn't documented yet, but if you do this for each of your lakes, it 
should: 

1. Speed up creation of the lakemorphometry object
2. Speed up the calculation of the metrics. 
3. And, most importantly, fix the NA return on the maximum depth (at least it 
   did for you 1 lake example).  At this time I am not sure why the cropped DEM
   with the larger extent is returning NA.  Need to dig into that.

These steps estimate a reasonable buffer distance (using the lakeMajorAxisLength 
function), buffer the lake with that distance, then crop the DEM to the extent 
of the buffered lake.  

```{r}
tst_1majorlength <- lakeMajorAxisLength(lakeMorphoClass(tst_1lakes), F)
tst_1buffer <- gBuffer(tst_1lakes, width = tst_1majorlength)
tst_1dem <- crop(tst_dem, tst_1buffer)
```

# Create and plot the lakemorpho object

Now we can create the `lakemorpho` object with the lakes and the cropped DEM.

```{r}
tst_1lm <- lakeSurroundTopo(tst_1lakes, tst_1dem)
plot(tst_1lm)
```

# Calculate the metrics

Lastly, we can calculate the volume:

```{r}
tst_1volume <- lakeVolume(tst_1lm)
tst_1volume
```

Don't use the `calcLakeMetrics` function for this.  There is a bug in how it is doing lakeVolume.  I know what it is but haven't yet fixed it.